\documentclass{fast-nuces-bs}

\usepackage{blindtext}
\usepackage{mathptmx}% Times Roman font
\usepackage[T1]{fontenc}
\usepackage{lipsum} 
\usepackage{sectsty}
\usepackage{tikz-uml}
\usepackage{titlesec}
\usepackage{adjustbox}
\usepackage{listings}
\usepackage{color}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}

\lstset{style=mystyle}

% Information about the Thesis 
% -----------------------------------------------------------------------------
% (All are compulsory, do not delete any line other than author Information)
% For e.g., usually there are 3 students in a group, so leave authorone, 
% authortwo, and authorthree, and delete authorfour.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\department{Department of Computer Science}
\faculty{Computer Science}
\degreeyear{2018}
\degreemonth{May}
\degreename{Computer Science}
\campuscity{Peshawar}
\authorone{Aziz Ullah}{p14-6111}
\authortwo{Najeeb Khan}{p14-6112}
\authorthree{Hafiz Saud Arshad}{p14-6097}
%\authorfour{John Cena}{p15-6789}
\supervisor{Dr. Omar Usman Khan}
\sessionduration{2014-2018}
\cosupervisor{Dr. Mohammad Nauman}
\deanname{Dr. Hasina Khatoon}
\directorname{Dr. Tariq Khan}
\hodname{Dr. Omar Usman Khan}
\fypcoordinatorname{Shakir Ullah}
\title{Real Time Pakistani Sign Language
	Recognition Using Kinect}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Former document starts below this
\begin{document}

\begin{acknowledgements}
	We are very thankful to Almighty Allah who is most Merciful and most Beneficent for
	giving us strength and courage to choose such challenging project and for completing it
	with great dignity and grace. Lots of people played a significant role in the completion of
	this project.
	We firstly thanks Dr. Omar Usman Khan who motivated us to select this project. He
	encouraged and showed us the way the project can be implemented. He has been very
	kind, supportive and patience to us since the beginning of our project. His guidance and
	experience brought us on the right track when we lost again and again.
	We are highly thankful to all of our teachers who had been guiding us throughout our
	project work. Their knowledge, guidance, and training enabled us to carry out this development work more efficiently. We would like to thank all our friends, colleagues and
	family for their support, motivation, and suggestions about the project.
\end{acknowledgements}

\begin{abstract}
We propose a system that would translate Pakistan Sign Language to text in real time.
As a prototype, the system is limited to recognition of four pre-defined sentences. The system takes
input from a Kinect Camera device as a person practices signs in front of it. The system
generates the sentences on the screen being practiced in the sign. Our 
system uses depth information right from the Kinect device and computes the time-series
of a sign being practiced. The system is trained on the four sentences using Random Forest. It  evaluates the input sign on the model established after training and displays the sentence
against the sign practiced on the screen as suggested (predicted) by model. Our tests report an accuracy of 85\% using this approach. Our work can
be extended to commercial scale based on the schema proposed by the project.
\end{abstract}

\include{chapter1/chapter1}
\include{chapter2/chapter2}
\include{chapter3/chapter3}
\include{chapter4/chapter4}
\include{chapter5/chapter5}

\include{conclusions/conclusions}

\appendix
\include{appendix1/appendix1}
\include{appendix2/appendix2}

\bibliographystyle{plain}
\bibliography{bib} 
\addcontentsline{toc}{chapter}{References} 

\end{document}
